Constructing the transition graphs of interacting hysterons

### 2022-06-10 Paper_draft.tex
Added reference to base graphs figure in piece about base graphs
Reworked figure for base graphs for better readability & organisation by main loop

The idea of base graphs allows us to improve our method for generating candidate graphs. Namely, by first constructing all base graphs, and only then evaluating all possible avalanches for each base graph individually, we exclude the subgraphs of the type shown in Fig. \ref{fig:impossiblegraphs}b from the outset. Because the number of graphs for which the design inequalities need to be explicitly generated is then reduced, the base graph method has an improved efficiency compared to the naive approach. 

@@

@@

    \includegraphics[width=0.5\textwidth]{base_graphs.png}
    \caption{All possible base graphs for the two- and three-hysteron systems. a) All base graphs for $N=2$; since scrambling is not possible for $N=2$, the base graphs are the two Preisach graphs. b) Preisach graphs for $N=3$. c) Scrambled base graphs for N=3 that are possible for linear coupling. d) Scrambled base graphs that are possible for general, but not linear model.}

@@

@@

Scrambling entails that the ordering of switching fields can change throughout the graph. In order to discuss scrambling more explicitly, we here define the main loop as the series of up and down transitions connecting the two saturated states. In the Preisach model, the ordering of the main loop fixes the transitions throughout the transition graph, so that each main loop corresponds to a unique Preisach graph. Because the down boundary of the main loop has $N!$ permutations, there are $N!$ Preisach graphs for a system of $N$ hysterons.\\

>>>>

The idea of base graphs allows us to improve our method for generating candidate graphs. Namely, by first constructing all base graphs, and only then evaluating all possible avalanches for each base graph individually, we exclude the subgraphs of the type shown in Fig. \ref{fig:impossiblegraphs}b from the outset. Because the number of graphs for which the design inequalities need to be explicitly generated is then reduced, the base graph method has an improved efficiency compared to the naive approach. \\

@@

\begin{figure*}[ht!]

@@

    \includegraphics[width=0.8\textwidth]{base_graphs.png}
    \caption{All possible base graphs for the two- and three-hysteron systems. a) All base graphs for $N=2$; since scrambling is not possible for $N=2$, the base graphs are the two Preisach graphs. b) All Preisach (top) and scrambled (bottom) base graphs for $N=3$. Graphs on a gray background are possible for general, but not linear coupling.}

@@

\end{figure*}

@@

Scrambling entails that the ordering of switching fields can change throughout the graph. In order to discuss scrambling more explicitly, we here define the main loop as the series of up and down transitions connecting the two saturated states. In the Preisach model, the ordering of the main loop fixes the transitions throughout the transition graph, so that each main loop corresponds to a unique Preisach graph. Because the down boundary of the main loop has $N!$ permutations, there are $N!$ Preisach graphs for a system of $N$ hysterons (Fig.\ref{fig:basegraphs_n3}a-b).\\
